\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-02-14 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates in .tex and .bib

\begin{keyword} %% keywords here, in the form: keyword \sep keyword
  Viscous Instabilities \sep Mobility Ratio \sep Multi-fluid flows \sep Porous media \sep Finite Element Methods. \blue{(choose key-words that do represent the contents of the paper. State-of-the-art development -re key-words should be represented as literature review in the Introduction section.)}
\end{keyword}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The first example is a simple comparison between two cases using fixed mesh and mobility ratios of $1$ and $10$ respectively. The aspect ratio of the $2D$ domain is 2 and it favors viscous fingering effects while temperature is not taken into account (assume isothermal environment) and gravity effects are negligible. Fluid $1$ is initially injected from the left hand side with velocity $u_{inj}=1$. The domain is fully saturated with fluid $2$. At the outlet (right hand side) boundary pressure levels are set to zero while no slip boundary conditions are implied at the upper and lower part of the formation. Fixed time step sizes of $1 \times 10^{-3}$ for both the fixed meshes and the CFL number for this set of simulations is 5. The $P_{1}DGP_{2}$ element type with piecewise linear description of veleocity within each element and quadratic pressure representation as part of the OCVFEM method along with the discontinuous Galerkin method are implied and composing the mesh. Saturation is located at the pressure nodes. Five different regions of 5 distinct absolute permeabilities (K) are introduced (fig.\ref{fig:5regions_domain}). The red square region is saturated with a $50\%-50\%$ mixture of both phase $1$ and $2$.

@@

In fig.\ref{fig:3testcase} there is a comparison between a single and double injection of fluid $1$ into the formation. This time fluid $1$ is injected from both the left hand side and the upper left corner of the domain, at a velocity u=$0.5$ while the set up of the problem remains the same, the mobility ratio is $10$, and the adaptive and ustructured mesh is implied. The top layer is saturated with phase $2$, while the rest of the domain has a saturation of $0.1$. The major difference is located in the velocity fields (see fig.\ref{fig:vel_magn}) as the presence of this extra inlet increases the flow at the top layers.

@@

At this point is proper to mentioned the extreme case, see fig.{\ref{fig:4testcase}, when mobility ratio is even an order of magnitude higher, when MR=$100$. Even though a this case is unlikely to happen as the mobility ration of the existing fluids in the industry, it is a test-case that can illustrate the higher, faster and more profound development of instabilities.

>>>>

\begin{keyword} %% keywords here, in the form: keyword \sep keyword
 Multi-fluid flows \sep Viscous Instabilities \sep Mobility Ratio \sep Porous media \sep Finite Element Methods.
\end{keyword}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The first example is a simple comparison between two cases using fixed mesh and mobility ratios of $1$ and $10$ respectively. The aspect ratio of the $2D$ domain is 2 and it favors viscous fingering effects while temperature is not taken into account (assume isothermal environment) and gravity effects are negligible. Fluid $1$ is initially injected from the left hand side with velocity $u_{inj}=1$. The domain is fully saturated with fluid $2$. At the outlet (right hand side) boundary pressure levels are set to zero while no slip boundary conditions are implied at the upper and lower part of the formation. Fixed time step sizes of $1 \times 10^{-3}$ for both the fixed meshes and the CFL number for this set of simulations is $0.5$. The $P_{1}DGP_{2}$ element type with piecewise linear description of veleocity within each element and quadratic pressure representation as part of the OCVFEM method along with the discontinuous Galerkin method are implied and composing the mesh. Saturation is located at the pressure nodes. Five different regions of 5 distinct absolute permeabilities (K) are introduced (fig.\ref{fig:5regions_domain}). The red square region is saturated with a $50\%-50\%$ mixture of both phase $1$ and $2$.

@@

In fig.\ref{fig:3testcase} there is a comparison between a single and double injection of fluid $1$ into the formation. This time fluid $1$ is injected from both the left hand side and the upper left corner of the domain, at a velocity u=$0.5$ while the set up of the problem remains the same, the mobility ratio is $10$, and the adaptive and ustructured mesh is implied. The top layer is saturated with phase $2$, while the rest of the domain has a saturation of $0.1$. The major difference is located in the velocity fields (see fig.\ref{fig:vel_magn}) as the presence of this extra inlet increases the flow at the top layers. At this point is proper to mentioned the extreme case, see fig.{\ref{fig:4testcase}, when mobility ratio is even an order of magnitude higher, when MR=$100$. Even though a this case is unlikely to happen as the mobility ration of the existing fluids in the industry, it is a test-case that can illustrate the higher, faster and more profound development of instabilities. Also by focusing the grid resolution in the saturation front, \citet{christou2015}  demonstrated the explicit formation of ﬁngers formed due to the instability in the pressure ﬁeld and triggered by viscosity ratio. A comparison has also been made by using a low resolution element, the $P_{1}DG-P_{1}DG$. No ﬁngers could be observed due to mesh coarseness (ﬁngers were ob-served in ﬁner uniform and adaptive meshes).

@@
